---
title: "Getting Started with binomial"
author: "Ben Goldberg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Coin Tossing

The `"binomial"` R package implements functions for calculating probabilities of a binomial random variable and related calculations such as the probability distribution, the expected value, variance, etc.


## Binomial Distribution Statistics

The user can easily make a variety of calculations regarding binomial distributions as long as they know the number of trials (1st parameter) and the probability of success (2nd parameter). These statistics include: mean, variance, mode, skewness, and kurtosis.

Here are some examples:

```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

These functions can take in numeric scalars as well as vectors.

Another interesting function is `bin_choose()`. This function calculates the number of combinations in which k successes can occur in n trials.

```{r}
bin_choose(n = 5, k = 2)
```


## Probability Distribution Analysis

Use the function `bin_probability()` to calculate the probability of getting exactly k successes within n trials.

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

To see this type of data on a broader scale, you can use the function `bin_distribution()`:

```{r}
dist = bin_distribution(trials = 5, prob = 0.5)
plot(dist)
```

This calculates the probability of getting exactly k successes for all possible values of k. As you can see, there is a built-in plotting method to help visualize this data.

For even more info, use `bin_cumulative()` to see the cumulative probabilities of this distribution. The data type that is returned also comes with a built-in plotting method.

```{r}
dist = bin_cumulative(trials = 5, prob = 0.5)
plot(dist)
```



## Binomial Distribution Object

Use the method `bin_variable()` to create a binomial distribution object to easily store and visualize data regarding a custom distribution. This object comes with built-in print and summary methods.

```{r}
bin = bin_variable(trials = 10, p = 0.3)
summary(bin)
```
